Higgs Assisted Razor Search for Higgsinos at 100 TeV

### 2019-07-23 main.tex
Pushing overleaf changes

\title{Higgs Assisted Razor Search for Higgsinos at 100 TeV}
\author[a]{Adarsh Pyarelal}
\author[b]{and Shufang Su}
\affiliation[a]{School of Information, University of Arizona, Tucson, AZ 85718 , USA}
\affiliation[b]{Department of Physics, University of Arizona, Tucson, AZ 85718, USA}

@@

\abstract{%

  A 100 TeV proton-proton collider will be an extremely effective way to probe
  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).
  In this paper, we describe a search strategy  for discovering pair-produced
  Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV
  hadron collider that decay to Bino-like lightest supersymmetric particle
  (LSP) via intermediate $Z$ and SM Higgs bosons that in turn decay to a pair
  of leptons and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
  (Z\N_1)(h\N_1)\rightarrow bb\ell\ell+\N_1\N_1$. In addition, we examine the
  potential for machine learning techniques to boost the power of our searches.
  Using this analysis, Higgsinos up to 1.4 TeV can be discovered for Binos with
  masses of about
  0.9 TeV using 3000 fb$^{-1}$ of data. Additionally, Higgsinos up to 1.8
  TeV can be excluded for Binos with masses of about 1.4 TeV at 95\% C.L.   This search
  channel extends the multi-lepton search limits, especially in the region
  where the mass difference between Higgsino NLSP and Bino LSP is smaller.
 }

@@

The existence of dark matter provides unambiguous evidence of new physics
beyond the Standard Model (SM) of particle physics. Indeed, given that there is
far more dark matter in the Universe than there is baryonic matter, determining
its precise nature is one of the most exciting challenges in particle physics
today.  One promising group of candidate for dark matter is the class of stable
particles known as weakly interacting massive particles (WIMPs). These
particles arise naturally in many extensions of the SM that are motivated by
the need to stabilize the electroweak scale. One of the most studied extensions
to the SM is the Minimal Supersymmetric Standard Model (MSSM), which predicts a
`supersymmetric partner', or \emph{superpartner}, for each SM
particle\footnote{For a detailed review of the MSSM, see Ref.
\cite{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the
lightest supersymmetric partner (LSP) is predicted to be absolutely stable,
making it a good candidate for dark matter. The identity of the LSP is
determined by the mass hierarchy of the superpartners, which in turn depends on
how supersymmetry is broken.  However, taking into account experimental
constraints and phenomenological considerations, the lightest of the  MSSM
particles known as the neutralinos emerges as the most attractive candidates
for the LSP \cite{Bertone:2004pz}.

@@

% Point to review papers for enumeration of studies
The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos) depend
on the hierarchy of the MSSM parameters $M_1, M_2$, and $\mu$~\footnote{For our
study, we assume all the mass parameters are positive.  For the current
analyses, the results do not depend much on the sign of those parameters.},
which roughly determine the masses of the Bino, Winos, and Higgsinos,
respectively~\cite{Han:2013kza}.  In this paper, we consider the Higgsino NLSP
and Bino LSP scenario with $M_1 < \mu \ll M_2$.  One of the motivations for
studying Higgsinos is that the parameter $\mu$ that governs its mass plays an
important role in electroweak symmetry breaking~\cite{Acharya:2014pua}, which
tends to be small by naturalness considerations.   Finding Higgsinos has
traditionally been more challenging than finding Winos, due to their smaller
production rate. This, however, can be remedied by the increased  production
cross sections and luminosities at a 100 TeV $pp$ collider.

>>>>

\title{Higgs Assisted Razor Search for Higgsinos at 100 TeV}
\author[a]{Adarsh Pyarelal}
\author[b]{and Shufang Su}
\affiliation[a]{School of Information, University of Arizona, Tucson, AZ 85721 , USA}
\affiliation[b]{Department of Physics, University of Arizona, Tucson, AZ 85718, USA}

@@

\abstract{% 
  A 100 TeV proton-proton collider will be an extremely effective way to probe
  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).
  In this paper, we describe a search strategy  for discovering pair-produced
  Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV
  hadron collider that decay to Bino-like lightest supersymmetric particle
  (LSP) via intermediate $Z$ and SM Higgs bosons that in turn decay to a pair
  of leptons and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
  (Z\N_1)(h\N_1)\rightarrow bb\ell\ell+\N_1\N_1$. In addition, we examine the
  potential for machine learning techniques to boost the power of our searches.
  Using this analysis, Higgsinos up to 1.4 TeV can be discovered for Binos with
  masses of about
  0.9 TeV using 3000 fb$^{-1}$ of data. Additionally, Higgsinos up to 1.8
  TeV can be excluded for Binos with masses of about 1.4 TeV at 95\% C.L.   This search
  channel extends the multi-lepton search limits, especially in the region
  where the mass difference between Higgsino NLSP and Bino LSP is small.
}

@@

The existence of dark matter provides unambiguous evidence of new physics
beyond the Standard Model (SM) of particle physics. Indeed, given that there is
far more dark matter in the universe than there is baryonic matter, determining
its precise nature is one of the most exciting challenges in particle physics
today.  One promising group of candidate for dark matter is the class of stable
particles known as weakly interacting massive particles (WIMPs). These
particles arise naturally in many extensions of the SM that are motivated by
the need to stabilize the electroweak scale. One of the most studied extensions
to the SM is the Minimal Supersymmetric Standard Model (MSSM), which predicts a
`supersymmetric partner', or \emph{superpartner}, for each SM
particle\footnote{For a detailed review of the MSSM, see Ref.
\cite{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the
lightest supersymmetric partner (LSP) is predicted to be absolutely stable,
making it a good candidate for dark matter. The identity of the LSP is
determined by the mass hierarchy of the superpartners, which in turn depends on
how supersymmetry is broken.  However, taking into account experimental
constraints and phenomenological considerations, the lightest of the MSSM
particles known as the neutralinos emerges as the most attractive candidate
for the LSP \cite{Bertone:2004pz}.

@@

% Point to review papers for enumeration of studies
The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos) depend
on the hierarchy of the MSSM parameters $M_1, M_2$, and $\mu$~\footnote{For our
study, we assume all the mass parameters are positive.  For the current
analyses, the results do not depend much on the sign of those parameters.},
which roughly determine the masses of the Bino, Winos, and Higgsinos,
respectively~\cite{Han:2013kza}.  In this paper, we consider the Higgsino NLSP
and Bino LSP scenario with $M_1 < \mu \ll M_2$.  One of the motivations for
studying Higgsinos is that the parameter $\mu$ that governs its mass plays an
important role in electroweak symmetry breaking~\cite{Acharya:2014pua}, and
is driven to be relatively small by naturalness considerations. 
Finding Higgsinos has traditionally been more challenging than finding Winos,
due to their smaller production rate.
This, however, can be remedied by the increased production cross sections and 
luminosities at a 100 TeV $pp$ collider.
